Mixed effect tweedie model in TMB

### 2019-04-08 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
change seed and add model configurations

set.seed(39201114)
```

@@

@@

@@

```{r}
d_fit$log_temperature_c <- log(d_fit$temperature_c)
m_temp4 <- sdmTMB(d_fit, log_temperature_c ~ 0 + as.factor(year) + poly(depth_scaled, 3),
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

@@

```{r}
aic <- function(m) {
  k <- length(m$model$par)
  nll <- m$model$objective
  2 * k - 2 * (-nll)
}
aic(m_temp1)
aic(m_temp2)
aic(m_temp3)
aic(m_temp4)
aic(m_temp5)
```

@@

```{r}
predictions3_nd <- predict(m_temp3, newdata = sdmTMB::qcs_grid)
saveRDS(predictions3_nd$data, file = "qcs-temp.rds")
```

@@

#FIXME: p_withheld$data$temperature_c is all zeros?!?!?! 
# temp work around (first make sure both df in same order)
arrange(p_withheld$data, fishing_event_id) 
arrange(d_withheld, fishing_event_id) 
p_withheld$data$temperature_c <- d_withheld$temperature_c
```

```{r}
ggplot(p_withheld$data, aes(est, temperature_c)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3,12) +
  ylim(3,12) +
  geom_abline()
```

>>>>

#set.seed(39201114) # original seed, predictions max out at .88 cor with true temp
set.seed(392011149)
```

@@

```{r}
m_temp3_rw_sp <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + poly(depth_scaled, 3),
  include_spatial = TRUE, ar1_fields = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE)

predictions3_rw_sp <- predict(m_temp3_rw)
predictions3_rw_sp$data$residuals <- residuals(m_temp3_rw)
```

```{r}
m_temp3_st <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + poly(depth_scaled, 3),
  include_spatial = TRUE, ar1_fields = TRUE, spatial_trend = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE)

predictions3_st <- predict(m_temp3_st)
predictions3_st$data$residuals <- residuals(m_temp3_st)
```

```{r}
ggplot(predictions3$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

@@

```{r}
ggplot(predictions3_st$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

@@

```{r}
d_fit$log_temperature_c <- log(d_fit$temperature_c)
m_temp4 <- sdmTMB(d_fit, 
  log_temperature_c ~ 0 + as.factor(year),
  time_varying = ~ 0 + poly(depth_scaled, 3),
  #time_varying =  ~ 0 + depth_scaled,
  include_spatial = TRUE, ar1_fields = TRUE, spatial_trend = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

@@

```{r}
aic <- function(m) {
  k <- length(m$model$par)
  nll <- m$model$objective
  2 * k - 2 * (-nll)
}
aic(m_temp1)
aic(m_temp2)
aic(m_temp3)
aic(m_temp3_rw)
aic(m_temp3_st)
aic(m_temp4)
aic(m_temp5)
```

@@

```{r}
predictions3_nd <- predict(m_temp3, newdata = sdmTMB::qcs_grid)
#saveRDS(predictions3_nd$data, file = "qcs-temp.rds")
```

@@

#FIXME: p_withheld$data$temperature_c is all zeros?!?!?! 
# temp work around (first make sure both df in same order)
arrange(p_withheld$data, fishing_event_id) 
arrange(d_withheld, fishing_event_id) 
p_withheld$data$temperature_c <- d_withheld$temperature_c

cor(p_withheld$data$est, p_withheld$data$temperature_c)^2 # 0.88 in first 
```

```{r}
ggplot(p_withheld$data, aes(temperature_c,est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3,15) +
  ylim(3,15) +
  geom_abline()
```

```{r}
m_temp3_rw$model$par
# 2 * plogis(m_temp1$model$par[["ar1_phi"]]) - 1
exp(m_temp3_rw$model$par[["ln_phi"]])

p_withheld_rw <- predict(m_temp3_rw, newdata = d_withheld)

#FIXME: p_withheld$data$temperature_c is all zeros?!?!?! 
# temp work around (first make sure both df in same order)
arrange(p_withheld_rw$data, fishing_event_id) 
arrange(d_withheld, fishing_event_id) 
p_withheld_rw$data$temperature_c <- d_withheld$temperature_c

cor(p_withheld_rw$data$est, p_withheld_rw$data$temperature_c)^2 # 0.86?
```

```{r}
ggplot(p_withheld_rw$data, aes(temperature_c,est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3,15) +
  ylim(3,15) +
  geom_abline()
```

```{r}
m_temp3_st$model$par
# 2 * plogis(m_temp1$model$par[["ar1_phi"]]) - 1
exp(m_temp3_st$model$par[["ln_phi"]])

p_withheld_st <- predict(m_temp3_st, newdata = d_withheld)

#FIXME: p_withheld$data$temperature_c is all zeros?!?!?! 
# temp work around (first make sure both df in same order)
arrange(p_withheld_st$data, fishing_event_id) 
arrange(d_withheld, fishing_event_id) 
p_withheld_st$data$temperature_c <- d_withheld$temperature_c

cor(p_withheld_st$data$est, p_withheld_st$data$temperature_c)^2
```

```{r}
ggplot(p_withheld_st$data, aes(temperature_c,est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3,15) +
  ylim(3,15) +
  geom_abline()
```

```{r}
m_temp4$model$par
# 2 * plogis(m_temp1$model$par[["ar1_phi"]]) - 1
exp(m_temp4$model$par[["ln_phi"]])

p_withheld4 <- predict(m_temp4, newdata = d_withheld)

#FIXME: p_withheld$data$temperature_c is all zeros?!?!?! 
# temp work around (first make sure both df in same order)
arrange(p_withheld4$data, fishing_event_id) 
arrange(d_withheld, fishing_event_id) 
p_withheld4$data$temperature_c <- d_withheld$temperature_c

cor(p_withheld4$data$est, p_withheld4$data$temperature_c)^2 # 0.86
```

```{r}
ggplot(p_withheld4$data, aes(log(temperature_c),est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(1, 3) +
  ylim(1, 3) +
  geom_abline()
```
